Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-09-01 src/tex/ms.tex
Testing matplotlib
fix plot font
Update ms.tex

\documentclass[twocolumn]{aastex631}

@@

With the modification we implemented, the amplitude ratio of the left-handed and right-handed polarizations becomes 
\begin{equation}
    \frac{h_\mathrm{L_{obs}}}{h_\mathrm{R_{obs}}}=\frac{\left(1-\cos\iota\right)^2}{\left(1+\cos\iota\right)^2}\exp\left({2\kappa\frac{d_C}{1\mathrm{Gpc}}\frac{f}{100\mathrm{Hz}}}\right)\,,
\end{equation}
where $h_\mathrm{L_{obs}}$ and $h_\mathrm{R_{obs}}$ are the observed Fourier amplitude of left-handed and right-handed polarizations of the GWs.
As the amplitude ratio does not only depends on $iota$ with this modification, but also $\kappa$ and $d_C$,
the PE on $\iota$ and $d_C$ are affected. Note that GR is recovered if $\kappa$ is $0$.

For some previous studies on the birefringence property such as \citet{Maria_2021}, they assume the effect of birefringence is independent of the frequency,
which is a zeroth-order approximation of the birefringence model in Chern-Simons gravity.
This would create a degeneracy between kappa and iota, as they can affect the amplitude ratio in the same way.
To reconstruct the amplitude ratio from the interferometer data, an $\iota$ representing a more face-off inspiral can pair with a positive $\kappa$,
or an $\iota$ representing a more face-on inspiral with a negative $\kappa$.
As a result, many pairs of $\iota$ and $\kappa$ can be plausible with the frequency independence.

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
This frequency dependence provides stronger enhancement or suppression from the birefringence to high frequency components of the GW, and visa versa.
Also, the frequency dependence can break the degeneracy between kappa and iota,
as this would make the effect of the birefringence affect the amplitude ratio differently compared to iota.
To illustrate the frequency dependence of amplitude birefringence,
the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.

>>>>

% \documentclass[aps,prd,twocolumn,superscriptaddress,preprintnumbers,floatfix,nofootinbib]{revtex4-2}
\documentclass[reprint,amsmath,amssymb,aps,twocolumn]{aastex631}

@@

With the modification we implemented, the amplitude ratio of the left-handed and right-handed polarizations becomes 
\begin{equation}
    \frac{h_\mathrm{L_{obs}}}{h_\mathrm{R_{obs}}}=\frac{\left(1-\cos\iota\right)^2}{\left(1+\cos\iota\right)^2}\exp\left({2\kappa\frac{d_C}{1\mathrm{Gpc}}\frac{f}{100\mathrm{Hz}}}\right)\,,
\end{equation}
where $h_\mathrm{L_{obs}}$ and $h_\mathrm{R_{obs}}$ are the observed Fourier amplitude of left-handed and right-handed polarizations of the GWs.
As the amplitude ratio does not only depends on $\iota$ with this modification, but also $\kappa$ and $d_C$,
the PE on $\iota$ and $d_C$ are affected. Note that GR is recovered if $\kappa$ is $0$.

For some previous studies on the birefringence property such as \citet{Maria_2021}, they assume the effect of birefringence is independent of the frequency,
which is a zeroth-order approximation of the birefringence model in Chern-Simons gravity.
This would create a degeneracy between $\kappa$ and $\iota$, as they can affect the amplitude ratio in the same way.
To reconstruct the amplitude ratio from the interferometer data, an $\iota$ representing a more face-off inspiral can pair with a positive $\kappa$,
or an $\iota$ representing a more face-on inspiral with a negative $\kappa$.
As a result, many pairs of $\iota$ and $\kappa$ can be plausible with the frequency independence.

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
This frequency dependence provides stronger enhancement or suppression from the birefringence to high frequency components of the GW, and visa versa.
Also, the frequency dependence can break the degeneracy between $\kappa$ and $\iota$,
as this would make the effect of the birefringence affect the amplitude ratio differently compared to $\iota$.
To illustrate the frequency dependence of amplitude birefringence,
the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.
